Towards a classification framework for social machines

### 2013-02-22 latex/paper_new.tex
Split dendrograms into two images

\begin{table*}[htbp]
\begin{center}
\begin{tabular}{|p{18cm}|}
\hline
{\bf Designed Affordances} \\
\hline
Domain specificity [1 - Specific / 5 - General] vs \\
\hspace{0.66cm} Generality of Purpose \\
Visibility and importance of a participants `reputation' [1 - Not important / 5- Important] \\
\hspace{0.66cm} Explicit representation of participant reputation [1 - No Reputations / 5 - Reputations] \\
Participants can define new types of contributions [1 - Not possible / 5 - Complete freedom] \\
Degree of open source software used/created [1 - Proprietary / 5 - Entirely open source] \\
Degree of openness and availability of data created in the system (APIs/Dumps) [1 - Closed/unavailable data / 5 - Completely open data] \\
Variety of actions participants can perform [1 - Single Action / 5 - Large variety of actions] \\
\hline
{\bf Participatory Affordances} \\
\hline
(Level of social features) - Supports social interaction [1 - No social features / 5 - Large variety of social features] \\
How often a participant participates (times a day, etc) [1 - Many times a day / 5 Seldom] \\
Importance of Timely Participation [1 - Unimportant / 5 - Timely] \\
Generality of Audience [1 - Niche / 5 - General] \\
Participant anonymity [1 - No Anonymity / 5 - Complete Anonymity] \\
Participant autonomy (1 - No autonomy / 5 - Complete autonomy) \\
Quality of participant contributions [1 - Low quality / 5 - High quality] \\
(Different roles clearly defined) - \\
\hspace{0.66cm} Clear separation of roles/responsibilities among participants - [1 - Single role - Everyone is the same) / 5 - People assume different roles/responsibilities] \\
	Extent of hierarchical organisation of roles [1 - No Hierarchy / 5 - Deep/Well-defined Hierarchy] \\
Variety of types of contributions [1 - Single Type / 5 - Large variety of types] \\
Participants are motivated by extrinsic award  [1 - Disagree / 5 - Agree] \\
Participants are intrinsically motivated [1 - Disagree / 5 - Agree] \\
Service/Platform derives benefit from participant participation [1 - Disagree /  5- Agree] \\
Participants directly benefit from participating [1 - Disagree / 5 - Agree] \\
Participants' friends/social network benefit from participation [1 - Disagree / 5 - Agree] \\
Participation is for the benefit of a specific person/group other than the participant or platform owner [1-Disagree / 5-Agree] \\
Participation is for the benefit of society/the world at large  [1 - Disagree / 5 - Agree] \\
Participation is done to `get something done' [1-Disagree/5-Agree] \\
Participation is done `for fun' [1-Disagree/5-Agree] \\
Participation is done to exchange knowledge [1-Disagree/5-Agree] \\
Participation is done to be social [1-Disagree/5-Agree] \\
Participation is done via mobile devices [1-Never / 5 - Often] \\
Participants' (geographic) location is used by the service [1-No / 5 - Very] \\
\hline
{\bf Analytics} \\
\hline
Popularity [1 - Unpopular / 5 - Very Popular] \\
Maturity [1 - New / 5 - Mature] \\
Ratio of passive to active participants [1 - Passive / 5 - Active] \\
Number of competitors [1 - Not Many / 5 - Many] \\
Extent of global geographic coverage [1 - Highly localised / 5 - Global]\\
\hline
\end{tabular}
\end{center}
\caption{Constructs of social machines, listing affordances that are designed into machines, affordances that have resulted from use, and analytical constructs that can be measured and change over time.} \label{table:constructs}
\end{table*}%

@@

\begin{figure*}
\begin{center}
\includegraphics[width=18cm]{img/dendrogram.png}
\caption{Dendrogram from a repertory grid exercise of the top 20 (ranked by Alexa) social machines from our element set, against our consolidated constructs.} \label{dendrogram}
\end{center}
\end{figure*}

>>>>

\begin{table*}[htbp]
\begin{center}
\begin{tabular}{|p{18cm}|}
\hline
{\bf Designed Affordances} \\
\hline
Domain specificity [1 - Specific / 5 - General] \\
Visibility and importance of a participants `reputation' [1 - Not important / 5- Important] \\
Explicit representation of participant reputation [1 - No Reputations / 5 - Reputations] \\
Participants can define new types of contributions [1 - Not possible / 5 - Complete freedom] \\
Degree of open source software used/created [1 - Proprietary / 5 - Entirely open source] \\
Degree of openness and availability of data created in the system (APIs/Dumps) [1 - Closed/unavailable data / 5 - Completely open data] \\
Variety of actions participants can perform [1 - Single Action / 5 - Large variety of actions] \\
\hline
{\bf Participatory Affordances} \\
\hline
Supports social interaction [1 - No social features / 5 - Large variety of social features] \\
How often a participant participates (times a day, etc) [1 - Many times a day / 5 Seldom] \\
Importance of Timely Participation [1 - Unimportant / 5 - Timely] \\
Generality of Audience [1 - Niche / 5 - General] \\
Participant anonymity [1 - No Anonymity / 5 - Complete Anonymity] \\
Participant autonomy (1 - No autonomy / 5 - Complete autonomy) \\
Quality of participant contributions [1 - Low quality / 5 - High quality] \\
Clear separation of roles/responsibilities among participants - [1 - Single role - Everyone is the same) / 5 - People assume different roles/responsibilities] \\
Extent of hierarchical organisation of roles [1 - No Hierarchy / 5 - Deep/Well-defined Hierarchy] \\
Variety of types of contributions [1 - Single Type / 5 - Large variety of types] \\
Participants are motivated by extrinsic award  [1 - Disagree / 5 - Agree] \\
Participants are intrinsically motivated [1 - Disagree / 5 - Agree] \\
Service/Platform derives benefit from participant participation [1 - Disagree /  5- Agree] \\
Participants directly benefit from participating [1 - Disagree / 5 - Agree] \\
Participants' friends/social network benefit from participation [1 - Disagree / 5 - Agree] \\
Participation is for the benefit of a specific person/group other than the participant or platform owner [1-Disagree / 5-Agree] \\
Participation is for the benefit of society/the world at large  [1 - Disagree / 5 - Agree] \\
Participation is done to `get something done' [1-Disagree/5-Agree] \\
Participation is done `for fun' [1-Disagree/5-Agree] \\
Participation is done to exchange knowledge [1-Disagree/5-Agree] \\
Participation is done to be social [1-Disagree/5-Agree] \\
Participation is done via mobile devices [1-Never / 5 - Often] \\
Participants' (geographic) location is used by the service [1-No / 5 - Very] \\
\hline
{\bf Analytics} \\
\hline
Popularity [1 - Unpopular / 5 - Very Popular] \\
Maturity [1 - New / 5 - Mature] \\
Ratio of passive to active participants [1 - Passive / 5 - Active] \\
Number of competitors [1 - Not Many / 5 - Many] \\
Extent of global geographic coverage [1 - Highly localised / 5 - Global]\\
\hline
\end{tabular}
\end{center}
\caption{Constructs of social machines, listing affordances that are designed into machines, affordances that have resulted from use, and analytical constructs that can be measured and change over time.} \label{table:constructs}
\end{table*}%

@@

\begin{figure}
\begin{center}
\includegraphics[width=4cm]{img/dendrogram-elements.png}
\caption{Dendrogram of elements (social machines) from a repertory grid exercise of the top 20 (ranked by Alexa) social machines from our element set, against our consolidated constructs.} \label{dendrogram}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{img/dendrogram-constructs.png}
\caption{Dendrogram of constructs from a repertory grid exercise of the top 20 (ranked by Alexa) social machines from our element set, against our consolidated constructs.} \label{dendrogram}
\end{center}
\end{figure}
